---
title: "sketchpad_basic"
output: html_document
---

# Import some libraries 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggthemes)
library(coda)
library(xtable)

# library(lme4)
# # Note: to install langcog, 
# library(langcog)
library(jsonlite)

sumlogprob <- function(a, b) {
  if(a>b) {
    return(a+log1p(exp(b-a)))
  } else{
    return(b+log1p(exp(a-b)))
  }
}
```

# Load in all the flattened output

```{r}
splits <- c(1,3,4,5) # 2,
# models <- c('human', 'multimodal_conv42', 'multimodal_fc6', 'multimodal_pool1')
#variants <- 
combined <- data.frame(perception = c(), infWeight = c(), simScaling = c(), 
                       pragWeight = c(), costWeight = c(), logLikelihood = c(),
                       split = c())
for (split in splits) {
  file <- paste0(c('balancedavg', split, '.csv'), collapse = '')
  path <- paste0(c('..', 'models', 'enumerateOutput', file), collapse = '/')
  combined <- rbind(combined, read_csv(path) %>% mutate(split = split))
}
```

# Explore priors

```{r}
comparison.df <- data.frame(comparison = c(), BF = c())
```

```{r}
## Noticed that for some reason, some files duplicated param levels so we use `distinct` to remove duplicates
posterior = combined %>%
  group_by(split) %>%
  distinct() %>% 
  mutate(logPriorProb = -log(length(loglikelihood))) %>%
  mutate(normalizingConstant = reduce(loglikelihood, sumlogprob)) %>%
  mutate(logPosteriorProb = loglikelihood - normalizingConstant) 

```

Examine difference in perception model, collapsing over params

* Within human, test informativity & cost

```{r}
## First, restrict to human and normalize everything to sum to 1
humanPosterior <- posterior %>%
  group_by(split) %>%
  filter(perception == 'human') %>%
  mutate(logPosteriorProb = logPosteriorProb - reduce(logPosteriorProb, sumlogprob),
         logPriorProb = -log(length(logPriorProb))) #%>% summarize(a = reduce(logPriorProb, sumlogprob), b = reduce(logPosteriorProb, sumlogprob))

## Next, consider nested 'no pragmatics' model and integrate over nuisance params to get Bayes Factor
comparison.df = rbind(
  comparison.df, 
  humanPosterior %>%
    filter(pragWeight == 0) %>%
    summarize(posterior = reduce(logPosteriorProb, sumlogprob),
              prior = reduce(logPriorProb, sumlogprob)) %>% 
    mutate(BF = log10(1/exp(posterior - prior))) %>%
    select(-posterior, -prior) %>%
    mutate(comparison = 'human_pragVSnoprag')
)
```

```{r}
## Next, consider nested 'no cost' model and integrate over nuisance params to get Bayes Factor=
comparison.df = rbind(
  comparison.df, 
  humanPosterior %>%
    filter(costWeight == 0) %>%
    summarize(posterior = reduce(logPosteriorProb, sumlogprob),
              prior = reduce(logPriorProb, sumlogprob)) %>% 
    mutate(BF = log10(1/exp(posterior - prior))) %>%
    mutate(comparison = 'human_costVSnocost') %>%
    select(-posterior, -prior)
)
```

* compare three vision models

```{r}
modelPosterior <- posterior %>%
  group_by(split) %>%
  filter(perception != 'human') %>%
  mutate(logPosteriorProb = logPosteriorProb - reduce(logPosteriorProb, sumlogprob),
         logPriorProb = -log(length(logPriorProb))) #%>% summarize(a = reduce(logPriorProb, sumlogprob), b = reduce(logPosteriorProb, sumlogprob))

comparison.df = rbind(
  comparison.df, 
  modelPosterior %>%
    group_by(split, perception) %>%
    summarize(posterior = reduce(logPosteriorProb, sumlogprob)) %>% 
    spread(perception, posterior) %>%
    summarize(fc6VSconv42 = log10(exp(multimodal_fc6 - multimodal_conv42)),
              fc6VSpool1  = log10(exp(multimodal_fc6 - multimodal_pool1))) %>%
    gather(comparison, BF, fc6VSconv42, fc6VSpool1)
)
```

* Within best vision model, test informativity & cost...

```{r}
fc6Posterior <- posterior %>%
  filter(perception == 'multimodal_fc6') %>%
  mutate(logPosteriorProb = loglikelihood - reduce(loglikelihood, sumlogprob),
         logPriorProb = -log(length(logPriorProb))) #%>% summarize(a = reduce(logPriorProb, sumlogprob), b = reduce(logPosteriorProb, sumlogprob))

comparison.df = rbind(
  comparison.df, 
  fc6Posterior %>%
    filter(pragWeight == 0) %>%
    summarize(posterior = reduce(logPosteriorProb, sumlogprob),
              prior = reduce(logPriorProb, sumlogprob)) %>% 
    mutate(BF = log10(1/exp(posterior - prior))) %>%
    select(-posterior, -prior) %>%
    mutate(comparison = 'fc6_pragVSnoprag')
)
```

```{r}
## Next, consider nested 'no cost' model and integrate over nuisance params to get Bayes Factor=
comparison.df = rbind(
  comparison.df, 
  fc6Posterior %>%
    filter(costWeight == 0) %>%
    summarize(posterior = reduce(logPosteriorProb, sumlogprob),
              prior = reduce(logPriorProb, sumlogprob)) %>% 
    mutate(BF = log10(1/exp(posterior - prior))) %>%
    select(-posterior, -prior) %>%
    mutate(comparison = 'fc6_costVSnocost')
)
```

Make table

```{r}
table <- comparison.df %>% 
  group_by(comparison) %>% 
  do(rbind(., data.frame(
    split = 'median', 
    BF = median(.$BF), 
    comparison = first(.$comparison)
  ))) %>% 
  spread(comparison, BF) %>%
  rename(`cost (fc6)` = fc6_costVSnocost,
         `context (fc6)` = fc6_pragVSnoprag,
         `cost (human)` = human_costVSnocost,
         `context (human)` = human_pragVSnoprag,
         `fc6 vs. conv42` = fc6VSconv42,
         `fc6 vs. pool1` = fc6VSpool1) %>%
  xtable() 

names( table ) <- sapply(names(table), function(x) {
  if(x == 'split') {
    return('split') 
  } else {
    return (paste0(c('\\multicolumn{1}{p{0.35in}}{\\centering ', x, '}'),
            collapse = ''))
  }
}, USE.NAMES = F)
print(table, include.rownames=FALSE, sanitize.colnames.function=function(x){x})
```

Visualize marginals w/ facet plot

```{r}

estimate_mode <- function(s) {
  d <- density(s)
  return(d$x[which.max(d$y)])
}
HPDhi<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","upper"])
}
HPDlo<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

```{r}
samples = humanPosterior %>%
    mutate(posterior = exp(logPosteriorProb)) %>%
    filter(posterior > 0.0001) %>%
    mutate(n = floor(posterior*10000)) %>%
    do(data.frame(.[rep(1:nrow(.), .$n),])) %>%
    select(-perception, -n, -posterior, -loglikelihood, -logPosteriorProb, -logPriorProb, -normalizingConstant) %>%
    gather(parameter, value) #%>%
    #mutate(value = as.numeric(as.character( value)))

samples %>%
  group_by(parameter) %>%
  summarize(mode = estimate_mode(value),
            md_lo = round(HPDlo(value), 3),
            md_hi = round(HPDhi(value), 3))

ggplot(samples, aes(x = value))+
  geom_density(aes(y=..density..), adjust = 0.05) +
    # geom_histogram(aes(y=..density..), 
    #              data =subset(samples, parameter == "alpha" ), 
    #              binwidth = .25, colour="black", fill="white") +
    # geom_histogram(aes(y=..density..), 
    #              data=subset(samples, parameter == "beta"), 
    #              binwidth = .05, colour="black", fill="white") +
    # geom_density(aes(y=..density..),
    #              data =subset(samples, parameter == "alpha" ), 
    #              adjust = 2, alpha=.2, fill="#FF6666")+
    # geom_density(aes(y=..density..),
    #              data=subset(samples, parameter == "beta"), 
    #              adjust = 5, alpha=.2, fill="#FF6666")+
    facet_wrap(~ parameter, scales = 'free') +
    theme_few(10)
```

# Explore predictives

```{r}
# helpers


dogs <- c('weimaraner', 'chihuahua', 'basset', 'doberman', 'bloodhound', 'bullmastiff', 'goldenretriever', 'pug')
chairs = c('leather', 'straight', 'squat', 'sling', 'woven', 'waiting', 'inlay','knob')
birds = c('crow', 'pigeon', 'robin', 'sparrow', 'tomtit', 'nightingale', 'bluejay', 'cuckoo')
cars = c('beetle', 'bluesport', 'brown', 'white', 'redsport', 'redantique', 'hatchback', 'bluesedan')
```

```{r}
predictives <- read_csv('./bdaOutput/human_combined_costPredictives.csv') %>%
  group_by(coarseGrainedTrueSketch, coarseGrainedPossibleSketch) %>%
  summarize(modelProb = reduce(modelProb, sumlogprob) - log(length(modelProb))) %>%
  rename(trueSketch = coarseGrainedTrueSketch, possibleSketch = coarseGrainedPossibleSketch) %>%
  separate(trueSketch, into = c('trueCondition','trueSketchTarget'), remove = F) %>%
  separate(possibleSketch, into = c('possibleCondition','possibleSketchTarget'), remove = F) 
```

Sanity check: higher probability assigned to true condition than false?

```{r}
predictives %>%
  group_by(trueSketch, trueCondition, possibleCondition) %>%
  summarize(modelProb = reduce(modelProb, sumlogprob) - log(length(modelProb))) %>%
  group_by(trueCondition, possibleCondition) %>%
#  mutate(totalProb = exp(reduce(modelProb, sumlogprob) - log(length(modelProb))))
  summarize(modelProb = sum(exp(modelProb))) %>% # - log(length(modelProb))) %>%
  ggplot(aes(x = trueCondition, y = modelProb, fill = possibleCondition)) +
      geom_bar(position = 'dodge', stat = 'identity') +
      theme_few() +
      scale_fill_colorblind()
```

### Make ranking curve

```{r}
pcts <- data.frame(topn = c(NA), further = c(NA), closer = c(NA))
num = 1
for(num in seq(1, 62, 1)) {
  nums <- predictives %>% 
    group_by(trueSketch, trueCondition) %>%
    top_n(num, modelProb) %>%
    select(trueSketch, possibleSketch, trueCondition, modelProb) %>%
    group_by(trueSketch, trueCondition) %>%
    summarize(containsTrueSketch = length(intersect(trueSketch, possibleSketch)) > 0) %>%
    group_by(trueCondition) %>%
    summarize(num = mean(containsTrueSketch)) %>%
    spread(trueCondition, num)
  pcts <- rbind(pcts, c(num, nums$further, nums$closer))
}
```

```{r}
ggplot(pcts %>% gather(trueCondition, val, further, closer), aes(x = topn, y = val, linetype=trueCondition, color = trueCondition)) +
  geom_line() +
  #geom_point()
  #theme_few() +
  #geom_vline(xintercept = 2) +
  theme_few() +
  ylim(0,1) +
  xlim(1,4) +
  xlab('k') +
  ylab('% of trials where true sketch\n is in top k (out of 64)') +
  theme(aspect.ratio = .5)

ggsave('test.png')
```

### Visualize confusion matrix

```{r}
confusion <- predictives %>% #left_join(predictives, sketchTargets, by = c('possibleSketch')) %>% 
    mutate(trueDomain = case_when(trueSketchTarget %in% chairs ~ 'chair',
                                  trueSketchTarget %in% dogs ~ 'dog',
                                  trueSketchTarget %in% birds ~ 'bird',
                                  trueSketchTarget %in% cars ~ 'car',
                                  T ~ 'other')) %>%
    mutate(possibleDomain = case_when(possibleSketchTarget %in% chairs ~ 'chair',
                                  possibleSketchTarget %in% dogs ~ 'dog',
                                  possibleSketchTarget %in% birds ~ 'bird',
                                  possibleSketchTarget %in% cars ~ 'car',
                                  T ~ 'other')) %>%
    select(trueCondition, possibleCondition, trueSketch, possibleSketch, trueSketchTarget,
           possibleSketchTarget, trueDomain, possibleDomain, modelProb)
#write_csv(confusion, 'supplementedPredictives.csv')
```

### By domain...

```{r}
errorsByDomain <- confusion %>%
  unite(trueDomainLabel, trueCondition, trueDomain, remove = F) %>%
  unite(possibleDomainLabel, possibleCondition, possibleDomain, remove = F) %>%
  group_by(trueSketch, trueDomain, possibleDomain, trueCondition, possibleCondition) %>% #trueDomainLabel,possibleDomainLabel, 
  summarize(prob = reduce(modelProb, sumlogprob) - log(length(modelProb))) %>%
  spread(possibleCondition, prob) %>%
  group_by(trueCondition, possibleDomain, trueDomain) %>% 
  summarize(diff=sum(exp(closer) - exp(further))) #%>%
  

ggplot(errorsByDomain, aes(x = possibleDomain, y = desc(trueDomain), fill = diff)) +
  geom_tile() +
  facet_wrap(~ trueCondition) +
  theme(aspect.ratio = 1, axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_fill_gradient2()
  
ggsave('context-sensitivity-by-domain.png')
```

### By object...

This is good -- higher probability assigned to sketches of true object within a domain than of other objects in the domain (and even higher than of objects in other domains)

Note: probably better to do some kind of within-class comparison here, like subtract off other

```{r}
targetProbs <- confusion %>% filter(trueSketchTarget == possibleSketchTarget)

errorsByObj <- confusion %>%
  group_by(trueSketch, possibleSketch,
           trueCondition, possibleCondition, 
           trueSketchTarget,possibleSketchTarget,
           trueDomain, possibleDomain) %>%
  summarize(prob = reduce(modelProb, sumlogprob) - log(length(modelProb))) %>%
  ungroup() %>%
  arrange(trueCondition, possibleCondition,trueDomain, possibleDomain, trueSketchTarget,possibleSketchTarget) %>% 
  mutate(trueSketchTarget = factor(trueSketchTarget, unique(trueSketchTarget)),
         possibleSketchTarget = factor(possibleSketchTarget, unique(possibleSketchTarget)))

confusion %>% 
  mutate(sameDomain = ifelse(trueDomain == possibleDomain, 'same', 'different')) %>%
  mutate(sameObject = ifelse(trueSketchTarget == possibleSketchTarget, 'same', 'different')) %>%
  mutate(sameCondition = ifelse(trueCondition == possibleCondition, 'same', 'different')) %>%
  group_by(trueSketch,sameDomain, sameObject, sameCondition) %>%
  summarize(prob = exp(reduce(modelProb, sumlogprob))) #%>%
  # group_by(trueSketch) %>% 
  #group_by(trueDomain, trueCondition, sameDomain, sameObject, sameCondition) %>%
  #summarize(prob = exp(sum(prob)))
```

Now try visualizing the finer-grained confusion matrix

```{r}
errorsByObj %>%
  group_by(trueSketch, possibleCondition, trueCondition, possibleSketchTarget, trueSketchTarget) %>%
  summarize(prob = reduce(prob, sumlogprob) - log(length(prob))) %>%
  spread(possibleCondition, prob) %>%
  group_by(trueCondition, possibleSketchTarget, trueSketchTarget) %>% 
  summarize(diff=sum(exp(closer) - exp(further))) %>%
  #arrange(trueDomain, possibleDomain) %>% 
ggplot(aes(x = trueSketchTarget, y = possibleSketchTarget, fill = diff)) +
  geom_tile() + 
  geom_vline(xintercept = seq(8.5, 8.5*10, 8)) +
  #geom_hline(yintercept = c(-8.5, -8.5*10, -8)) +
 facet_wrap(~ trueCondition) +
  theme(aspect.ratio = 1,  axis.text.x = element_text(size=rel(0.5), angle = 90, hjust = 1)) %>%
  scale_fill_gradient2()

#ggsave('confusion-by-object.png')
```

Zoom in on one object to examine finer level detail, e.g. contexts?

```{r}
confusion %>% 
  filter(trueSketchTarget == 'bluejay') %>%
  filter(possibleSketchTarget == 'bluejay') %>%
  arrange(trueCondition, possibleCondition) %>% 
  mutate(trueSketch = factor(trueSketch, unique(trueSketch)), 
         possibleSketch = factor(possibleSketch, unique(possibleSketch))) %>% 
  ggplot(aes(x = trueSketch, y = desc(possibleSketch), fill = modelProb)) + 
    geom_tile() 
```

# Supplemental analyses (now in python)

## Explore train-test split

```{r}
fullSketchData <- read_csv('RSA/bdaInput/sketchData_fixedPose.csv')
length(unique((d %>% separate(sketchLabel, into = c('gameid','trialNum')))$gameid))
splitTestExamples <- read_csv('RSA/bdaInput/split-by-condition-test-examples.txt', col_names = F) %>%
  rename(sketchLabel = X1) 
length(unique((splitTestExamples %>% separate(sketchLabel, into = c('gameid','trialNum')))$gameid))

fullSketchData %>% left_join(splitTestExamples %>% separate(sketchLabel, into=c('gameid', 'trialNum'), remove=F) %>% group_by(gameid) %>% mutate(n = n()) %>% mutate(prop = n/32)) %>%
  ggplot(aes(x = prop)) + geom_histogram()

fixedPose
d <- raw_fixed %>% 
  mutate(gameid = str_sub(gsub("-", "", gameID), start = -12)) %>%
  mutate(sketchLabel = sprintf('%s_%s', gameid, trialNum)) %>%
  select(sketchLabel, condition, target, Distractor1, Distractor2, Distractor3, mean_intensity, pose) 

```

## Analyze raw similarities

Load in different embeddings and make boilerplate iterables for them

```{r}
pragSimilarities <- fromJSON('./refModule/json/similarity-human.json', flatten = T)

lookupPragSimilarity <- function(object, sketch) {
  return(pragSimilarities[[object]][[sketch]])
}
```

Add columns for the different kinds of similarity

```{r}
d.raw <- read_csv('./bdaInput/sketchData_fixedPose_splitbycontext_augmented2_pilot2.csv')
d.similarity <- d.raw %>%
  select(sketchLabel, Target) %>%
  complete(Target, sketchLabel) %>%
  rename(trueTarget = Target) %>%
  left_join(d.raw, by = c('sketchLabel')) %>%
  rename(sketchTarget = Target, sketchCondition = condition) %>%
  select(sketchLabel, sketchTarget, trueTarget, sketchCondition, coarseGrainedSketchInfo) %>%
  rowwise() %>%
  mutate(pragSimilarity = lookupPragSimilarity(trueTarget, sketchLabel)) %>%
  separate(trueTarget, into = c('garbage','garbage1','trueTarget'), remove = T) %>%
  separate(sketchTarget, into = c('garbage2','garbage3', 'sketchTarget'), remove = T) %>%
  mutate(trueDomain = case_when(trueTarget %in% chairs ~ 'chair',
                                trueTarget %in% dogs ~ 'dog',
                                trueTarget %in% birds ~ 'bird',
                                trueTarget %in% cars ~ 'car',
                                T ~ 'other')) %>%
  mutate(sketchDomain = case_when(sketchTarget %in% chairs ~ 'chair',
                                sketchTarget %in% dogs ~ 'dog',
                                sketchTarget %in% birds ~ 'bird',
                                sketchTarget %in% cars ~ 'car',
                                T ~ 'other')) 


```

### What is confusion matrix at level of pure object?

```{r}
d.similarity %>%
  group_by(sketchCondition,coarseGrainedSketchInfo,trueTarget,sketchTarget,trueDomain,sketchDomain) %>%
  summarize(meanSimilarity = mean(pragSimilarity), k = length(pragSimilarity)) %>%
  ungroup() %>%
  arrange(sketchCondition, trueDomain, sketchDomain, trueTarget, sketchTarget) %>% 
  mutate(trueTarget = factor(trueTarget, unique(trueTarget)),
         sketchTarget = factor(sketchTarget, unique(sketchTarget)),
         coarseGrainedSketchInfo = factor(coarseGrainedSketchInfo, unique(coarseGrainedSketchInfo))) %>%
  # group_by(trueTarget == sketchTarget, trueDomain == sketchDomain) %>%
  # summarize(mean(meanSimilarity))
ggplot(aes(x = coarseGrainedSketchInfo, y = trueTarget, fill = meanSimilarity)) +
  geom_tile() + 
  geom_vline(xintercept = seq(8.5, 8.5*10, 8)) +
  scale_fill_gradient(low = "black", high = "white") +
  geom_hline(yintercept = seq(8.5, 16*10, 8)) +
 # facet_wrap(~ condition) +
  theme(aspect.ratio = .5, axis.text.x = element_text(angle = 90, hjust = 1)) 

ggsave('raw-similarities.png')
```

## What's the difference between context conditions? 

Seems like embedding thinks 'far' sketches of the target are slightly more similar to the target than 'close' sketches (unintuitive)

```{r}
d.conditionDiff <- d.similarity %>%
  group_by(sketchCondition,coarseGrainedSketchInfo,trueTarget,sketchTarget,trueDomain,sketchDomain) %>%
  summarize(meanSimilarity = mean(pragSimilarity), k = length(pragSimilarity)) %>%
  ungroup() %>%
  select(sketchCondition, trueTarget, sketchTarget, trueDomain, sketchDomain, meanSimilarity) %>%
  spread(key = sketchCondition, value = meanSimilarity) %>%
  mutate(conditionDiff = closer - further) %>%
  arrange(trueDomain, sketchDomain, trueTarget, sketchTarget) %>% 
  mutate(trueTarget = factor(trueTarget, unique(trueTarget)),
         sketchTarget = factor(sketchTarget, unique(sketchTarget))) 

d.conditionDiff %>% 
  group_by(trueTarget == sketchTarget) %>%
  summarize(m = mean(conditionDiff))
```

Not a lot of structure overall

```{r}
ggplot(d.conditionDiff, aes(x = sketchTarget, y = desc(trueTarget), fill = conditionDiff)) +
    geom_tile() + 
    geom_vline(xintercept = seq(8.5, 8.5*10, 8)) +
    scale_fill_gradient(low = "black", high = "white") +
    # geom_hline(yintercept = seq(8.5, 16*10, 8)) +
   # facet_wrap(~ condition) +
    theme(aspect.ratio = 1, axis.text.x = element_text(angle = 90, hjust = 1))+ 
  ggtitle('whiter when close similarity is higher')
```

Sanity check: is similarity higher for target object than other things?

```{r}
tmp %>%
  ggplot(aes(x = pragSimilarity, fill = contextElement)) +
    geom_density(alpha = .5) +
    theme_few() +
    theme(aspect.ratio = 1) +
    xlim(-1, 1) +
    ggtitle('sketch similarity in further condition') +
    facet_wrap(~ domain) +
    scale_fill_colorblind()

ggsave('diffconditions.pdf')
```

Yes,on 'far' conditions the sketch tends to be similar to the target and dissimilar to the distractors

What about closer condition? 

```{r}
tmp = d.similarity %>% 
  mutate(contextElement = case_when(contextElement == 'Target' ~ 'target',
                                    T ~ 'distractor')) %>%
  filter(condition == 'closer') 

tmp %>%
  ggplot(aes(x = pragSimilarity, fill = contextElement)) +
    geom_density(alpha = .5) +
    theme_few() +
    theme(aspect.ratio = 1) +
    xlim(-1, 1) +
    ggtitle('sketch similarity in close condition') +
    facet_wrap(~ domain) +
    scale_fill_colorblind()

ggsave('sameconditions.pdf')
```

On 'close' conditions the sketch tends to be similar to both...

What does the early layer look like?

```{r}
tmp = d.similarity %>% 
  mutate(contextElement = case_when(contextElement == 'Target' ~ 'target',
                                    T ~ 'distractor')) %>%
  filter(condition == 'further') 

tmp %>%
  ggplot(aes(x = earlySimilarity, fill = contextElement)) +
    geom_density(alpha = .5) +
    theme_few() +
    theme(aspect.ratio = 1) +
    xlim(-1, 1) +
    ggtitle('sketch similarity in further condition') +
    scale_fill_colorblind()

ggsave('early_far.pdf')
```

What does the early layer look like?

```{r}
tmp = d.similarity %>% 
  mutate(contextElement = case_when(contextElement == 'Target' ~ 'target',
                                    T ~ 'distractor')) %>%
  filter(condition == 'closer') 

tmp %>%
  ggplot(aes(x = earlySimilarity, fill = contextElement)) +
    geom_density(alpha = .5) +
    theme_few() +
    theme(aspect.ratio = 1) +
    xlim(-1, 1) +
    ggtitle('sketch similarity in closer condition') +
    scale_fill_colorblind()

ggsave('early_close.pdf')
```

But is anything different across conditions? We'd expect that your bird is pushed to look more like the target bird when the distractors are also birds... 

```{r}
wilcox.test(sketchSimilarity ~ condition, 
            data = d.similarity %>% filter(contextElement == 'Target'))

d.similarity %>% 
  filter(contextElement == 'Target') %>%
  separate(name, into = c('pureName', 'poseStr')) %>% #  = strsplit(name, split = '_')[0]) 
  group_by(condition, pureName) %>%
  summarize(m = mean(sketchSimilarity)) %>%
  spread(condition, m) %>%
  ggplot(aes(x = closer, y = further, label = pureName)) +
    # geom_point() +
    # geom_abline(slope = 1, intercept = 0) +
    geom_text(check_overlap = T) +
    theme_few() +
    theme(aspect.ratio = 1) +
    ggtitle('sketch similarity to target across conditions')
```

Not with this embedding... 

Correlation b/w embeddings at trial-by-trial level

```{r}
d.similarity %>% 
  filter(contextElement == 'Target') %>%
  separate(name, into = c('pureName', 'poseStr')) %>% #  = strsplit(name, split = '_')[0]) 
  #gather(embedding, similarity, strictSimilarity,nonstrictSimilarity) %>%
  # group_by(embedding, pureName) %>%
  # summarize(m = mean(sketchSimilarity)) %>%
  # spread(condition, m) %>%
  ggplot(aes(x = strictSimilarity, y = nonstrictSimilarity)) +#, label = pureName)) +
    geom_bin2d() +
    # geom_abline(slope = 1, intercept = 0) +
    #geom_text(check_overlap = T) +
    theme_few() +
    theme(aspect.ratio = 1) +
    ggtitle('sketch similarity to target across conditions')
```

Correlation b/w embeddings at item level

```{r}
d.similarity %>% 
  filter(contextElement == 'Target') %>%
  separate(name, into = c('pureName', 'poseStr')) %>% #  = strsplit(name, split = '_')[0]) 
  gather(embedding, similarity, strictSimilarity,nonstrictSimilarity) %>%
  group_by(embedding, pureName) %>%
  summarize(m = mean(similarity)) %>%
  spread(embedding, m) %>%
  ggplot(aes(x = strictSimilarity, y = nonstrictSimilarity, label = pureName)) +
    #geom_smooth(method = 'loess') +
    geom_text(check_overlap = T) +
    geom_abline(slope = 1, intercept = 0) +
    #geom_text(check_overlap = T) +
    theme_few() +
    theme(aspect.ratio = 1) +
    xlim(-.2, 1) +
  ylim(-.2, 1) +
    ggtitle('sketch similarity to target across embeddings')
```


## Create BDA input

### Import group data

TODO: incorporate pilot0 as well (though missing pose data makes this nontrivial)

```{r}
raw <-  read_delim('sketchpad_basic_merged_group_data.csv', delim = ',') 
invalid_trials <- (read_csv('./invalid_trial_paths.txt', col_names = F) %>%
  mutate(X1 = gsub('gameID_', '', X1)) %>%
  mutate(X1 = gsub('trial_', '', X1)) %>%
  mutate(X1 = gsub('.png', '', X1)) %>%
  mutate(X1 = str_sub(gsub("-", "", X1), start = 25)))$X1


d <- raw %>% 
  mutate(gameid = str_sub(gsub("-", "", gameID), start = -12)) %>%
  mutate(sketchLabel = sprintf('%s_%s', gameid, trialNum)) %>%
  filter(iteration == 'pilot1') %>% # Just use pilot 1 for now
  filter(!(sketchLabel %in% invalid_trials)) %>% # Remove invalid sketch (e.g. w/ text)
  filter(outcome == 1) %>% # Remove incorrect trials
  select(sketchLabel, condition, target, Distractor1, Distractor2, Distractor3, mean_intensity, pose) %>%
  mutate(domain = case_when(target %in% chairs ~ 'chair',
                            target %in% dogs ~ 'dog',
                            target %in% birds ~ 'bird',
                            target %in% cars ~ 'car',
                            T ~ 'other'))
```

```{r}
with_domain <- raw %>%
  mutate(domain = case_when(target %in% chairs ~ 'chair',
                            target %in% dogs ~ 'dog',
                            target %in% birds ~ 'bird',
                            target %in% cars ~ 'car',
                            T ~ 'other')) 
write_csv(with_domain %>% select(-X1, -`Unnamed: 0`), 'merged_data_plus_domain.csv')
```

Write out cost look-up table (use mean_intensity for now):

```{r}
as.list(setNames(d$mean_intensity,d$sketchLabel)) %>%
  write_json('RSA/refModule/json/costs.json')
```

We reorder contexts alphabetically because we just care about content of set. Also reformat object names to include pose.... 

```{r}
d$context = apply(d %>% select(Distractor1, Distractor2, Distractor3), 1, 
                  function(x) paste(sort(x), collapse="_"))

d.ordered = d %>% 
  select(-Distractor1, -Distractor2, -Distractor3) %>%
  separate(context, into = c('Distractor1', 'Distractor2', 'Distractor3')) %>%
  mutate(Target = sprintf("%s_%04d", target, pose)) %>%
  mutate(Distractor1 = sprintf("%s_%04d", Distractor1, pose)) %>%
  mutate(Distractor2 = sprintf("%s_%04d", Distractor2, pose)) %>%
  mutate(Distractor3 = sprintf("%s_%04d", Distractor3, pose))
```

Note: it'd be nicer if we had a smaller space of unique conditions for quicker BDA in webppl, but pretty much every trial was unique due to the pose randomization... 

## Model comparison

Compute likelihood for each model... 

```{r}

View()
View(rbind(
  read_csv('./bdaOutput/pure_S0_MCMCParams.csv', col_types = 'cccdddddd') %>% mutate(dataset = 'S0'),
  read_csv('./bdaOutput/pure_S1_MCMCParams.csv', col_types = 'cccdddddd')%>% mutate(dataset = 'S1'),
  read_csv('./bdaOutput/combined_MCMCParams.csv', col_types = 'cccdddddd') %>% mutate(dataset = 'combined')
))
modelOutput = rbind(
  read_csv('./bdaOutput/pure_S0_MCMCParams.csv', col_types = 'cccdddddd') %>% mutate(dataset = 'S0'),
  read_csv('./bdaOutput/pure_S1_MCMCParams.csv', col_types = 'cccdddddd')%>% mutate(dataset = 'S1'),
  read_csv('./bdaOutput/combined_MCMCParams.csv', col_types = 'cccdddddd') %>% mutate(dataset = 'combined')
) %>%
  group_by(dataset, perception,pragmatics, production) %>%
  summarize(prob = reduce(logLikelihood, sumlogprob) - log(length(logLikelihood)))

View(  read_csv('./bdaOutput/S0_vs_S1_bareParams.csv', col_types = 'cccdddddd') %>% mutate(dataset = 'bare'))
print(modelOutput)
```

Visualize as bars

```{r}
ggplot(modelOutput %>% ungroup() %>% mutate(pragmatics = ordered(pragmatics, levels = c('S0', 'S1'))), 
aes(x = pragmatics, y = prob, fill = production)) +
    geom_bar(stat = 'identity', position = 'dodge', width = .75) +
    guides(fill=guide_legend(title="Speaker model")) +
    ylab('log-likelihood') +
    scale_fill_colorblind() +
    theme_few(12) +
    #theme(aspect.ratio = )
    coord_cartesian(ylim=c(-7500, -8000)) +
    theme(legend.position = 'top') 

ggsave('modelComparison.pdf')
```

```{r}
samples = read_csv('./bdaOutput/S1_coarsenedParams.csv', col_types = 'cccdddddd') %>%
  filter(pragmatics == 'S1' & production == 'cost') %>%
  filter(posteriorProb != -Inf) %>%
  mutate(posteriorProb = as.numeric(posteriorProb)) %>%
  mutate(intermed = exp(posteriorProb - max(posteriorProb))) %>%
  mutate(posteriorProb = log(intermed/sum(intermed))) %>%
  select(-intermed, -pragmatics, -production) %>%
  mutate(prob = exp(posteriorProb)) %>%
  filter(prob > 0.001) %>%
  mutate(n = floor(prob*1000)) %>%
  do(data.frame(.[rep(1:nrow(.), .$n),])) #%>%
  select(-t, -n, -prob) %>%
  gather(parameter, value) %>%
  mutate(value = as.numeric(as.character( value)))
```
 
```{r}
fixedSimilarities <- fromJSON('./RSA/refModule/json/strict-similarity-pragmatics-fixedpose-conv4_2.json', flatten = T)

raw_fixed <- read_delim('sketchpad_basic_pilot2_group_data.csv', delim = ',') 

d <- raw_fixed %>% 
  mutate(gameid = str_sub(gsub("-", "", gameID), start = -12)) %>%
  mutate(sketchLabel = sprintf('%s_%s', gameid, trialNum)) %>%
  select(sketchLabel, condition, target, Distractor1, Distractor2, Distractor3, mean_intensity, pose) 
```

```{r}
d$context = apply(d %>% select(Distractor1, Distractor2, Distractor3), 1, 
                  function(x) paste(sort(x), collapse="_"))

test_trials <- (read_csv('./pilot2_test_examples.txt', col_names = F) %>%
  mutate(X1 = gsub('gameID_', '', X1)) %>%
  mutate(X1 = gsub('trial_', '', X1)) %>%
  #mutate(X1 = gsub('.png', '', X1)) %>%
  mutate(X1 = str_sub(gsub("-", "", X1), start = 25)) %>%
  separate())$X1


d.ordered = d %>% 
  select(-Distractor1, -Distractor2, -Distractor3) %>%
  separate(context, into = c('Distractor1', 'Distractor2', 'Distractor3')) %>%
  mutate(Target = sprintf("%s_%04d", target, pose)) %>%
  mutate(Distractor1 = sprintf("%s_%04d", Distractor1, pose)) %>%
  mutate(Distractor2 = sprintf("%s_%04d", Distractor2, pose)) %>%
  mutate(Distractor3 = sprintf("%s_%04d", Distractor3, pose))

as.list(setNames(d$mean_intensity,d$sketchLabel)) %>%
  write_json('RSA/refModule/json/costs.json')

# Only keep close trials from held-out set
d.ordered %>% 
  select(condition, sketchLabel, Target, Distractor1, Distractor2, Distractor3) %>%
  
  write_csv('./RSA/bdaInput/sketch_data.csv')
```

## How many repeated contexts in fixed pose version?

```{r}
fixedPose <- read_csv('RSA/bdaInput/sketchData_fixedPose.csv') %>%
  separate(sketchLabel, into = c('gameid', 'trialNum'))

fixedPose$context = apply(fixedPose %>% select(Target, Distractor1, Distractor2, Distractor3), 1, 
                  function(x) paste(sort(x), collapse="_"))

fixedPose %>% group_by(gameid, context) %>% summarize(trialNum = first(trialNum)) %>% group_by(context) %>% tally() %>% group_by(n) %>% tally()
# fixedPose.ordered = fixedPose %>% 
#   select(-Target, -Distractor1, -Distractor2, -Distractor3) %>%
#   separate(context, into = c('Target', 'Distractor1', 'Distractor2', 'Distractor3'))

fixedPose %>% group_by(Target, Distractor1, Distractor2, Distractor3) %>% tally() %>% group_by(n) %>% tally()
```

# Marginalize over posterior predictive

```{r}
meta <- read_csv('../models/bdaOutput/multimodal_full25k_combined_cost_splitbyobjectParams.csv', col_types = cols())
dir <- "../models/bdaOutput/predictives/"
makedf <- function(x) {
  print(x)
  return (read_csv(paste0(c(dir, x), collapse='/'), col_types = cols()) %>%
    select(-Target, -Distractor1, -Distractor2, -Distractor3) %>%
    mutate(sampleNum = strsplit(x, 'Predictives.csv')[[1]])) %>%
    spread(coarseGrainedPossibleSketch, modelProb)
}

df <- list.files(dir) %>%
  map(makedf) %>%
  reduce(rbind)

df.long <- df %>% 
  left_join(meta %>% 
              mutate(sampleNum = as.character(id)) %>% 
              select(sampleNum, posteriorProb)) %>%
  gather(possibleSketch, modelProb, closer_basset : further_woven)

out <- df.long %>%
  group_by(trueSketch, possibleSketch, coarseGrainedTrueSketch) %>%
  mutate(weighted = posteriorProb + modelProb) %>%
  summarize(weighted = reduce(weighted, sumlogprob)) 

out %>%  
  spread(possibleSketch, weighted) %>%
  separate(coarseGrainedTrueSketch, into = c('trueCondition', 'trueClass')) %>%
  write_csv('~/Downloads/out.csv')
```
